An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-06-24 CMPSpaper_writing/CMPSpaper_writing.Rmd
fixed a typo and prepare for tagging CC

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019],  in particular, Hamby set 252 and Hamby set 44. 
For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels. Two bullets are fired from each barrel, making up a set of 20 reference bullets. An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant. The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from. The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}. During the firing process, grooves and lands are engraved on a bullet. Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison. For algorithmic purposes, 
3D topographical images land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile). The x3p format provides a standard way of exchanging 2D and 3D profile data. It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/]  adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science. Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel. Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State. These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel.  Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].

>>>>

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019],  in particular, Hamby set 252 and Hamby set 44. 
For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels. Two bullets are fired from each barrel, making up a set of 20 reference bullets. An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant. The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from. The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}. During the firing process, grooves and lands are engraved on a bullet. Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison. For algorithmic purposes, 
3D topographical images of land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile). The x3p format provides a standard way of exchanging 2D and 3D profile data. It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/]  adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science. Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel. Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State. These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.  Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
